\documentclass{letter}[11pt]

\textheight 25cm
\topmargin-2cm
\evensidemargin-.3cm
\oddsidemargin-.3cm
\textwidth16.5cm
\pagestyle{empty}
\usepackage{url}

\signature{Gabriel Peyr\'e}
\address{Gabriel Peyr\'e\\
Ceremade, Universit\'e Paris-Dauphine,\\
email: {\tt gabriel.peyre@ceremade.dauphine.fr}}

\begin{document}

\begin{letter}{Pr. S.R. Arridge \\
Editor in Chief, Inverse Problems \\
}

\opening{Dear Pr. S.R. Arridge,}

Together with my co-author Vincent Duval, I would like to submit the manuscript \emph{Sparse Spikes Deconvolution on Thin Grids} for consideration as a regular article in Inverse Problems. 

\medskip

\begin{enumerate}
	\item By the present letter, we certify that there is no other publication or submission with a significant overlap with the submission.
	\item I (Gabriel Peyr\'e) confirm  that my co-author (Vincent Duval) is aware of the current submission and consent to its review by IP.
	\item We have no conflict of interest, in particular no past collaboration with action editors of IP. 
	\item We believe that Otmar Scherzer or Martin Burger are the best suited editors to handle the reviewing process.
\end{enumerate}

\medskip

We suggest as reviewers the following people who are expert in the problem of sparse spikes deconvolution: Gongguo Tang, Kristian Bredies, Badri Narayan Bhaskar, Laurent Demanet, Markus Grasmair, Ben Recht, Carlos Fernandez-Granda. 

\medskip

We are aware that the present article is long, the reason being that we decided to present the theoretical analysis of two methods (Lasso and C-BP) in the same article. If the editor and the reviewers think it is preferable, it would be of course possible to split the article in two separate contributions. 

\medskip

Please let us know if we can be of further assistance to you.

\closing{Yours sincerely,} 



\end{letter}





\end{document}
